### 2015-05-15 ase-2015-tex/abstract.tex
Added information about test case generation.
Updated the abstract to mention new features. Moved limitations from conclusion to Symbolic Heaps section.:

A fundamental challenge of using symbolic execution for software
analysis is the treatment of dynamically allocated data. This paper
introduces a compact symbolic heap representation based on a field
sensitive points-to graph with edges annotated with disjunctive
formulas describing aliasing relationships, along with a set of
rewrite rules that describe the initialization, dereferencing, and
update to fields in the symbolic heaps. The symbolic heap supports
arbitrary recursive data structures and captures all possible heaps
that follow a common control flow path up to the point of
execution. An evaluation of a proof-of-concept implementation in the
Java Pathfinder framework is presented to demonstrate the
computational feasibility of the approach over several classical
symbolic execution benchmarks.

>>>>

A fundamental challenge of using symbolic execution for software analysis is the treatment of dynamically allocated data. Existing techniques either underapproximate the space of possible inputs or are computationally infeasible. For example, dynamic symbolic execution (DSE) handles symbolic dereferencing by substituting in a value from a valid concrete execution. Generalized symbolic execution (GSE) initiates a new search path for every possible aliasing configuration. This paper introduces a method for de-referencing and manipulating values in a true block-box symbolic input heap that overcomes the limitations of previous methods. The symbolic heap supports arbitrary recursive data structures and captures all possible heaps that follow a common control flow path up to the point of execution. Computation of complex preconditions and postconditions is supported, as well as automatic generation of test inputs. An evaluation of a proof-of-concept implementation in the Java Pathfinder framework is presented to demonstrate the computational feasibility of the approach over several classical symbolic execution benchmarks.

### 2015-05-15 ase-2015-tex/approach.tex
Updated the abstract to mention new features. Moved limitations from conclusion to Symbolic Heaps section.:

Application of complex method invariants is facilitated by repOk-style methods as described in~\cite{boyapati2002korat}.

@@

>>>>

Application of complex method invariants is facilitated by $\mathtt{repOk}$-style methods as described in~\cite{boyapati2002korat}.

@@

\subsection{Limitations}
This paper presents a symbolic heap that is both sound and complete with respect to the properties verifiable through symbolic execution. However, when the symbolic heap is used in conjunction with any analysis method, it is subject the limitations inherent to the underlying technique. For example, for programs that do not exhibit self-limiting behavior, as a practical matter symbolic execution generally requires some sort of bounds to limit infinite loops and recursion. This means that some sort of constraint will invariably be imposed by the symbolic execution engine, impacting the heap as it would any other symbolic value.  In this case, the advantage of our method is that these constraints may be freely chosen to suit the purposes of the analysis at hand, rather than being imposed by a limitation of the heap representation.

### 2015-05-15 ase-2015-tex/conclusion.tex
Updated the abstract to mention new features. Moved limitations from conclusion to Symbolic Heaps section.:

Although our approach is inspired by the work in the static analysis
domain, the heap representations used by those techniques do not lend
themselves to symbolic execution since they rely on approximations,
they are inflexible in what types of relations can be expressed, and
they rely on rewriting of constraints.  In this work, we present a
heap representation for symbolic execution that maintains exactness,
represents arbitrary heap structures without restrictions on aliasing
relationships, and supports dynamic on-the-fly initialization of heap
structures. This unique combination of capabilities enables the
symbolic heap algorithm to outperform state-of-the-art symbolic
execution techniques, and in some cases, the performance gains are
considerable. We believe that performance gains in symbolic execution
can naturally benefit a variety of analyses based on symbolic
execution, for example, verification of properties, especially those
related to the heap, test case generation, program evolution
techniques such as directed incremental symbolic
execution~\cite{person:pldi2011}, and other back-end analyses. In
future work we plan to evaluate the impact of analyses that rely on
symbolic execution.

>>>>

In this work, we present a
heap representation for symbolic execution that maintains exactness,
represents arbitrary heap structures without restrictions on aliasing
relationships, and supports dynamic on-the-fly initialization of heap
structures. This unique combination of capabilities enables the
symbolic heap algorithm to outperform state-of-the-art symbolic
execution techniques, and in some cases, the performance gains are
considerable. We believe that performance gains in symbolic execution
can naturally benefit a variety of analyses based on symbolic
execution, for example, verification of properties, especially those
related to the heap, test case generation, program evolution
techniques such as directed incremental symbolic
execution~\cite{person:pldi2011}, and other back-end analyses. In
future work we plan to evaluate the impact of analyses that rely on
symbolic execution.

### 2015-05-15 ase-2015-tex/intro.tex
Updated the abstract to mention new features. Moved limitations from conclusion to Symbolic Heaps section.:

An alternative approach which does not under-approximate the heap is
Generalized Symbolic Execution
(\gsetxt{})~\cite{Cadar:2008,KiasanKunit,GSE03,Rosner:2015}.  On symbolic
dereferencing operations,~\gsetxt{} partitions the input space between the
various possible aliasing configurations on-the-fly and also creates
non-deterministic choice points on the current path in order to
explore each heap configuration. \bah{This approach, however, is
inefficient because it initiates a new search path for every possible heap configuration.
The resulting path growth is exponential in the number of dereferencing operations.}

@@

This new symbolic heap and update rules for symbolic execution is a
novel approach for de-referencing and updating heap allocated data
that brings together the best features of previous work while removing
the limitations of that same work. Although it draws inspiration from
abstract interpretation by defining a symbolic heap,
\begin{compactitem}
  \item it is an exact representation, without over- or under-approximation;
  \item it imposes no restrictions on the set of heaps that can be defined;
  \item it does not require the creation of an initial set of input heaps;
  \item it is not tied to specific constraint solver theories, e.g., arrays; and
  \item it does not require global constraint rewriting for on-the-fly updates.
\end{compactitem}
These several properties set this work apart from other related works.

>>>>

An alternative approach which does not under-approximate the heap is
Generalized Symbolic Execution
(\gsetxt{})~\cite{Cadar:2008,KiasanKunit,GSE03,Rosner:2015}.  On symbolic
dereferencing operations,~\gsetxt{} partitions the input space between the
various possible aliasing configurations on-the-fly and also creates
non-deterministic choice points on the current path in order to
explore each heap configuration. This approach, however, is
inefficient because it initiates a new search path for every possible heap configuration.
The resulting path growth is exponential in the number of dereferencing operations.

@@

This new symbolic heap and update rules for symbolic execution is a
novel approach for de-referencing and updating heap allocated data
that brings together the best features of previous work while removing
the limitations of that same work. The symbolic heap has the following 
properties:
\begin{compactitem}
  \item constraints are neither over- or under-approximated;
  \item it does not restrict the set of heaps that can be defined;
  \item it does not require explicit construction of heap inputs;
  \item automatically computes path pre- and postconditions;
  \item generates path-coverage-optimal sets of test input heaps;
  \item it supports complex user-defined heap structure invariants 
\end{compactitem}
